---
title: "Exploring Global flows of international migrantion of scholars"
author: "Thiago Almeida"
format: html
---

# Introduction

```{r libraries}
#| message: false
#| include: false

# Loading packages that we need to use
library(tidyverse)
```

Let's use *Scopus* database to explore some potential outcomes of Quarto.

This database can be accessed in the main GitHub page from the project ([click here](https://github.com/MPIDR/Global-flows-and-rates-of-international-migration-of-scholars)).

```{r load_data}
#| message: false
#| include: false

# Loading data from SCOPUS database
data <- read_csv("../data_processed/scopus_2024_V1_scholarlymigration_countryflows_enriched.csv")

```

The database is structured such as is possible to see below:

```{r}
head(data)
```

## Flows over time

One of the possible questions to be answered is how is the behaviour of these flows over time when we think about outflows. The first step is to analyze the outflows based on the origin region of flow over time. The graphic below describes this relationship.

```{r}
#| echo: false

tab <- data %>% 
  summarise(
    n = sum(n_migrations),
    .by = c(year, regionfrom)
  )

tab %>% 
  ggplot() +
  aes(x = year, y = n, color = as.factor(regionfrom), group = as.factor(regionfrom)) %>% 
  geom_line() +
  scale_x_continuous(breaks = seq(min(tab$year)-1,max(tab$year)+1,2)) +
  theme_linedraw() +
  labs(
    color = "Region of origin",
    x = "Year",
    y = "Number of migrant flows",
    title = "Scholar migrant flows by origin regions over time - World, 1998-2018.",
    caption = "MPIDR, Scholarly Migration Database."
  ) +
  theme(
    legend.title = element_text(face = "bold"),
    plot.title = element_text(face = "bold")
  )

```

Migrant flows have origin, mainly, in Europe and Central Asia, followed by North America, East Asia, and the Pacific. Although the relative importance of these regions for the global migrant flows remained similar over time, it is possible to see that Europe and Central Asia increased more than others since 2004-2005.